### 2011-03-09 docs/runtime_parameters/runtime_parameters.tex
slight tweaking
add the run time parameter use_linear_grav_in_beta.  this adds the option to use piecewise linear gravity in the integration of beta0

@@

>>>>

Table~\ref{table:runtime} lists the runtime parameters available to
all MAESTRO problems.  Problem-specific runtime parameters are not
shown here.

@@

\verb=  use_linear_grav_in_beta  = &   when integrating $\beta_0$, use a piecewise linear (.true.) representation of gravity or piecewise constant (.false.)  &  .false. \\
